|

### 2024-08-11 doc/presentation.qmd
output table 1 in presentation

+  To verify the robustness of descriptive statistics before the main replication, Table 1 from Leuz et al. was replicated, yielding results that closely align with the original study:
```{python}
#| label: table_1 
#| echo: false
#| output: asis

print(prep_latex_table(
    results['table_1'],
    caption='Replicated table - Descriptive statistics: Number of firm-year observations per country',
    label='tab:table_1'
))
```

>>>>

+  To verify the robustness of descriptive statistics before the main replication, Table 1 from Leuz et al. was replicated, yielding results that closely align with the original study:
---
```{python}
#| label: table_1 
#| echo: false
#| output: asis

print(prep_latex_table(
    results['table_1'],
    caption='Replicated table - Descriptive statistics: Number of firm-year observations per country',
    label='tab:table_1',
    fontsize='\\fontsize{5pt}{6pt}\\selectfont'  # Set smaller font size
))
```
